---
title: "string_practice"
author: "Charles Hendrickson"
date: "8/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
```

## Task 3: Practice with strings
Install the datapasta package (if you don’t have it already)
Restart R
Create a new .Rmd in your R folder called string_practice.Rmd
Copy all contents of the html table below to your clipboard:

-Replace the “Engr” with “Engineering” in the building column
-Separate the building column into two separate columns, building and wing, separated at the dash
-Only keep observations with the word “responded” in the alarm_message column
-Separate the message time from the rest of the message by separating at --
-Convert the date column to a Date class using lubridate

```{r}
alarm_report <- data.frame(
  stringsAsFactors = FALSE,
              date = c("2020-03-14", "2020-03-15", "2020-04-10", "2020-04-18"),
          building = c("Engineering-North",
                       "Bren Hall","Engineering-South","Engr-North"),
     alarm_message = c("10:02am – HVAC system down, facilities management alerted",
                       "8:24am – Elevator North out of service",
                       "12:41am – Fire alarm, UCSB fire responded and cleared",
                       "9:58pm – Campus point emergency siren, UCPD responded"))%>%
    mutate(building = str_replace(building, pattern = "Engr", replacement = "Engineering")) %>% 
  separate(building, c("building", "wing")) %>% 
  filter(str_detect(alarm_message, "responded")) %>% 
  separate(alarm_message, c("time", "message"), sep = "–") %>% 
  mutate(date = ymd(date))

```


















tibble::tribble(
         ~date,           ~building,                                              ~alarm_message,
  "2020-03-14", "Engineering-North", "10:02am – HVAC system down, facilities management alerted",
  "2020-03-15",         "Bren Hall",                    "8:24am – Elevator North out of service",
  "2020-04-10", "Engineering-South",     "12:41am – Fire alarm, UCSB fire responded and cleared",
  "2020-04-18",        "Engr-North",     "9:58pm – Campus point emergency siren, UCPD responded"
  )
